Learning and comparing functional connectomes between populations

### 2012-12-26 paper.tex
typo

Taking a difference stance on distributed variability, the ``network-based
statistics'' approach \cite{zalesky2010} draws from the hypothesis that
if, in a second-level analysis, an effect is detected in a connection
that lies in a network of strongly connected nodes, the whole network is
likely to cary an effect. Thus, they adapt cluster-level inference to
connectivity analysis, in order to mitigate the curse of multiple
comparisons.

>>>>

Taking a different stance on distributed variability, the ``network-based
statistics'' approach \cite{zalesky2010} draws from the hypothesis that
if, in a second-level analysis, an effect is detected in a connection
that lies in a network of strongly connected nodes, the whole network is
likely to cary an effect. Thus, they adapt cluster-level inference to
connectivity analysis, in order to mitigate the curse of multiple
comparisons.
